Giant Low Surface Brightness Galaxies As Merger Remnants

### 2015-04-16 glsb.tex
outline intro

\author{Peter Yoachim\altaffilmark{1}, Denise Shmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{1}, Victor P. Debattista\altaffilmark{3}
  }

@@

Meanwhile, observers tend to classify GLSB systems as normal spirals.  \citet{Das13} concludes that GLSB systems are an extreme form of late type spiral galaxies.  Similarly, \citet{Kasparova14} claim that the large dark matter scale of Malin~2 can explain it's features.

@@

@@

\citet{Ibata05} look at extended disk of M31.

\citet{Ibata13} claim M31 satellites are co-planer.

\citet{McConnachie09} M31 survey showing lots of merger structure.

Bothun of course has a nice web page with images at:  http://zebu.uoregon.edu/sb2.html

another nice image at http://www.capella-observatory.com/ImageHTMLs/Galaxies/UGC6614.htm

From \citet{Matthews01b}, \HI\ measurements on the gals:
%name          rms   Fmax W20   W50   HRV  e_HRV S\HI\  eS\HI\  S/N
%F 568-6    *  2.29  17.5 420   393   13829  7  4.20  0.64  7.6 
%UGC 6614   *  2.86  81.2 290   255    6351  2 15.94  0.72 28.4 
\citet{Matthews01b} also lists some incs values--calls Malin2 an Scd/Sd galaxy, has some good tables that are only available on-line.  I'll need to compare my stellar kinematics to the \HI\ kinematics.

@@

\citet{Schiminovich13}:  Observe \HI\ shells in ellipticals.

\citet{Iodice06}:  Nice minor and major axis observation of a polar-ring galaxy.

\citet{Brook08b}:  Makes a polar ring galaxy via extended accretion of cosmological gas.  They say polar disk galaxies are built just like the outskirts of regular galaxies, they just happen to be very mis-aligned.

@@

%/astro/store/scratch/tmp/yoachim/Research/GLSB/THINGS/guess_projen.py
\begin{figure}
\epsscale{0.5}
\plotone{Plots/things_projenguess.eps}
\epsscale{1}
\caption{Comparison of GLSB \HI\ masses \citep{Pickering97} with \HI\ masses measured in the THINGS survey \citep{Walter2008}.  While the \HI\ masses in the GLSB systems are high, they are consistent with what would be available in a merger with a V$_{\rm{max}}$\sim$110 km/s or smaller galaxy, assuming the merger did not trigger large amounts of star formation and feedback. \label{thingsMHI}}
\end{figure}

>>>>

\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{1}, Victor P. Debattista\altaffilmark{3}
  }

@@

Meanwhile, observers tend to classify GLSB systems as normal spirals.  \citet{Matthews01b} list Malin~2 as an Scd while \citet{Das13} concludes that GLSB systems are an extreme form of late type spiral galaxies.  Similarly, \citet{Kasparova14} claim that the large dark matter scale of Malin~2 can explain it's features.

@@

Points to cover in intro
\begin{itemize}
\item{GLSB galaxies are really big spirals}
\item{Typically classified as extreme spirals observaionally}
\item{but HST observations of Malin~1 show it is a regular galaxy with a distinct extended disk \citet{Barth07}}
\item{Models for GLSB formation}
  \begin{itemize}
  \item{regular growth (maybe like polar ring galaxies, or just the large end of spirals)}
  \item{faded collisional ring. \citet{Mapelli08, Mapelli12} }
  \item{high angular momentum accretion event. \citet{Pen06}}
  \end{itemize}
  \item{Discuss how, if GLSBs are merger remnents, they represent a unique possibility to trace the dark matter halo of elliptical galaxies.  }
\end{itemize}

@@

%\citet{Ibata05} look at extended disk of M31.
%\citet{Ibata13} claim M31 satellites are co-planer.  
%\citet{McConnachie09} M31 survey showing lots of merger structure.

%Bothun of course has a nice web page with images at:  http://zebu.uoregon.edu/sb2.html
%another nice image at http://www.capella-observatory.com/ImageHTMLs/Galaxies/UGC6614.htm

%From \citet{Matthews01b}, \HI\ measurements on the gals:
%name          rms   Fmax W20   W50   HRV  e_HRV S\HI\  eS\HI\  S/N
%F 568-6    *  2.29  17.5 420   393   13829  7  4.20  0.64  7.6 
%UGC 6614   *  2.86  81.2 290   255    6351  2 15.94  0.72 28.4 
%\citet{Matthews01b} also lists some incs values--calls Malin2 an Scd/Sd galaxy, has some good tables that are only available on-line.  I'll need to compare my stellar kinematics to the \HI\ kinematics.

@@

%\citet{Schiminovich13}:  Observe \HI\ shells in ellipticals.  
%\citet{Iodice06}:  Nice minor and major axis observation of a polar-ring galaxy.  
%\citet{Brook08b}:  Makes a polar ring galaxy via extended accretion of cosmological gas.  They say polar disk galaxies are built just like the outskirts of regular galaxies, they just happen to be very mis-aligned.

@@

%/astro/store/scratch/tmp/yoachim/Research/GLSB/THINGS/guess_projen.py
\begin{figure}
\epsscale{0.5}
\plotone{Plots/things_projenguess.eps}
\epsscale{1}
\caption{Comparison of GLSB \HI\ masses \citep{Pickering97} with \HI\ masses measured in the THINGS survey \citep{Walter2008}.  While the \HI\ masses in the GLSB systems are high, they are consistent with what would be available in a merger with a V$_{\rm{max}}\sim$110 km/s or smaller galaxy, assuming the merger did not trigger large amounts of star formation and feedback. \label{thingsMHI}}
\end{figure}
